A Systematic Approach to Analyzing Syndication of Viral News Stories

### 2019-12-06 paper/paper.tex
Update on Overleaf.

\section{Related Work}
There has been work done on early fake news detection by analyzing propagation paths and time series. Most of this work, however, has been limited in scope in terms of the domains that it covers, as well as the type of media being analyzed. For example, past research has focused on a either a few social media platforms, or a specific media outlet \cite{liu2018early},\cite{jin2014news}. The research that has spanned across multiple different domains of news (social media, various news outlets, etc.) has been limited in scope when considering the type of media that is being analyzed \cite{zannettou2018origins}.

@@

>>>>

\section{Related Work}
There has been work done on early fake news detection by analyzing propagation paths and time series, as well as analyzing the dynamics of news syndication. Most of this work, however, has been limited in scope in terms of the domains that it covers, as well as the type of media being analyzed. For example, past research has focused on a either a few social media platforms, a specific media outlet, or a single country \cite{liu2018early},\cite{jin2014news}, \cite{wang2009propagation}. The research that has spanned across multiple different domains of news (social media, various news outlets, etc.) has been limited in scope when considering the type of media that is being analyzed \cite{zannettou2018origins}. There has been little if any work done specifically on the syndication of viral news and trying to automatically analyze and track back a viral news story to its original publisher. The vast number of works on syndication mostly focus on content syndication from a marketing perspective.

@@

\subsection{Content Syndication in Marketing}
